Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-11-17 cbm-rbd-paper.tex
one-cycle total cost rate
updating section 5, graphs for different failure histories in paper, sim1cycle now returns all interesting stuff

\newcommand{\Rsysnow}{R^{(t_\text{now})}_\text{sys}}
\newcommand{\Tsysnow}{T^{(t_\text{now})}_\text{sys}}
\newcommand{\tsysnow}{t^{(t_\text{now})}_\text{sys}}
\newcommand{\fsysnow}{f^{(t_\text{now})}_\text{sys}}
\def\eknow{e_k^{(\tnow)}}
\def\cknow{c_k^{(\tnow)}}
\def\vectknow{\vec{t}_k^{(\tnow)}}
\def\Phinow{\Phi^{(\tnow)}}
\newcommand{\gnow}{g^{(\tnow)}}
\newcommand{\tausnow}{\tau_*^{(\tnow)}}
\newcommand{\tprep}{\tau_{\text{prep}}}

@@

Each operational cycle starts with system startup.
At this point in time, the system being is in an (as good as) new state,
i.e., all components in the system are (as good as) new and have not aged.
A cycle ends when the system is either maintained preventively, %at time $\tnow + \tausnow$ (on an absolute time scale),
or the system fails, which triggers a corrective maintenance action.

@@

At the end of each cycle,
the component information gained during the completed cycle is added to the component knowledge base
by updating the parameters $\nk$ and $\yk$ accordingly,
%using failure and censoring times as of the end of the cycle.
such that $\nkz$ and $\ykz$ for the following cycle account for the (censored) lifetimes observed during the previous cycle.
%We assume that both planned and unplanned maintenance action takes negligible time,
We assume that both a planned and unplanned maintenance action results in an (as good as) new system state by replacing all components,
such that the system begins a new cycle always under the same condition.
Replacement schemes that do not replace all components need to take into account the different ages of components in the system
at the start of a new cycle.
While this is in principle possible in our approach,
exploring such selective replacement schemes is out of scope for this paper,
since optimizing over replacement schemes is, in our view, a higly interesting topic on its own,
and we will comment on this in the Outlook (Section~\ref{sec:outlook}).

As we use a one-cycle criterion, the time both planned and unplanned maintenance actions require
does not matter directly for the determination of $\tausnow$.
Downtimes are instead accounted for indirectly via the costs parameters,
as described next.

@@

Let $\Tsysnow$ be the random variable corresponding to $\Rsysnow(t)$,
giving the (random) system failure time for times $t > \tnow$,
conditioned on all information available at $\tnow$,
and $\fsysnow(t)$ be the corresponding density.
Conditional on the realization of $\Tsysnow$, the unit cost rate is 
\begin{align*}
g(\tau \mid \Tsysnow = \tsysnow) &=
\begin{cases}
c_p / \tau  & \text{if } \tsysnow \ge \tau \\
c_u / \Tsys & \text{if } \tsysnow < \tau \,.
\end{cases}
\end{align*}
Taking the expectation over $\Tsysnow$ leads to the expected unit cost rate being
\begin{align}
\gnow(\tau) &= \E[g(\tau \mid \Tsysnow)] = \frac{c_p}{\tau} \Rsysnow(\tau) + c_u \int_0^\tau \frac{1}{t} \fsysnow(t) \dd t\,.
\label{eq:gtau}
\end{align}
Note that for the integral to exist in \eqref{eq:gtau},
$\E[1/\Tsysnow]$ must exist, which is a condition for $\fsysnow(t)$ for values of $t$ close to $0$ \citep{2006:coolen-schrijner-coolen}.
This restriction probably plays a role in the CBM literature's reluctance to adopt the one-cycle criterion.
For our approach, however, this condition is not relevant,
as we use a discrete approximation of $\Rsysnow(t)$ and $\fsysnow(t)$, respectively.
We will describe next how we numerically evaluate \eqref{eq:gtau} and find $\tausnow$.
%($\beta_k > 1$ $\forall k = 1,\ldots,K$ sufficient **???**)
%***here, $\Rsysnow(\cdot)$ shifted such that $\tnow = 0$.

@@

%*** not possible / *** to minimize $\gnow(\tau)$ analytically.
***we calculate $\Rsysnow(t)$ on discrete grid from $\tnow$ until some horizon time $\tnow + t_h$.
$t_h$ can be determined by practical considerations,
but generally should reach into the tail of $\Rsysnow(t)$.
We calculate $\gnow(\tau)$ on the same grid,
and determine $\tausnow$ as the minimum over this grid.

We approximate the integral in \eqref{eq:gtau} numerically by a sum,
where $\fsysnow(t)$ is calculated via differences of $\Rsysnow(t)$ values on a dense grid.
$\gnow(\tau)$ is likewise evaluated on a dense grid,
and $\tausnow = \arg\min \gnow(\tau)$ is determined as the minimum over the grid.
%The lower index $\tnow$ of the optimal moment of maintenance serves to remind that
%$\tau^*$ depends on $\tnow$, and also on the history of the system.

@@

***example figures with very weak prior info, could look different for stronger expert information!

@@

\begin{figure}
\includegraphics[width=\textwidth]{tauhistfig2}
\caption{$\tausnow$, $t^* = \tnow + \tausnow$, $\gnow(\tausnow)$, and the total cost rate **** as functions of $\tnow$
for the system depicted in Figure~\ref{fig:brakesys-layout},
assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$,
and $c_u = 1$, $c_p = 0.2$.
$\tausnow$ (top left panel) first decreases slightly, then remains more or less constant during failure-free periods,
dropping significantly at the failures of components $P_2$, $P_3$ and $H$ only.
If $\tprep = 0.5$, the drop of $\tausnow$ from $0.72$ to $0.38$ at $\tnow = 8$ would trigger a maintenance action
at (absolute) time $8.5$.
Since $\tausnow$ does not change dramatically most of the time, $t^*$,
the cost-optimal moment of maintenance on the absolute timescale (top right panel),
steadily increases, with small drops corresponding to drops in $\tausnow$,
indicating that as time progresses, accumulated information indicates that maintenance can be postponed.
Note that $\gnow(\tausnow)$ is the momentary cost rate relating to the expected residual lifetime (lower left panel),
differing from the overall cost rate (lower right panel).
%For the maintenance action triggered at $\tnow = 8$,
%the overall cost rate is $c_p / 8.5 = 0.024$ if the system does not fail until time $8.5$,
%and between $c_u / 8 = 0.125$ and $c_u / 8.5 = 0.118$ if the system fails.}
At time $8$, the overall expected cost rate for repair at time $8.38$ is $0.314$,
up from $0.076$ for repair at time $8.62$, as cost-optimal at time $7.9$.}
\label{fig:tauhistfig2}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{tauhistfig3}
\caption{Illustration of the gains due to the parameter update.
$\tausnow$ (top left panel) is consistently lower for the non-adaptive algorithm,
same with $t^*$ (top right panel).
The adaptive algorithm recongnizes the higher reliability of system components,
leading to lower current (lower left panel) and total (lower right panels) unit cost rates.}
\label{fig:tauhistfig3}
\end{figure}

***use simplified brake system from ASCE-ASME paper, example history of components failing

***plot both $\tau_*^{\tnow}$ and $\tnow + \tau_*^{\tnow}$ over time for different failure histories

>>>>

\newcommand{\Rsysnow}{R^{(t_\text{now})}_\text{sys}}
\newcommand{\Tsysnow}{T^{(t_\text{now})}_\text{sys}}
\newcommand{\tsysnow}{t^{(t_\text{now})}_\text{sys}}
\newcommand{\fsysnow}{f^{(t_\text{now})}_\text{sys}}
\def\eknow{e_k^{(\tnow)}}
\def\cknow{c_k^{(\tnow)}}
\def\vectknow{\vec{t}_k^{(\tnow)}}
\def\Phinow{\Phi^{(\tnow)}}
\newcommand{\gnow}{g^{(\tnow)}}
\newcommand{\tausnow}{\tau_*^{(\tnow)}}
\newcommand{\tprep}{\tau_{\text{prep}}}
\newcommand{\tstarnow}{t_*^{(\tnow)}}
\newcommand{\cstarnow}{c_*^{(\tnow)}}
\newcommand{\ctotalnow}{c_\text{total}^{(\tnow)}}

@@

Each operational cycle starts with system startup.
At this point in time, the system is in an (as good as) new state,
i.e., all components in the system are (as good as) new and have not aged.
A cycle ends when the system is either maintained preventively, %at time $\tnow + \tausnow$ (on an absolute time scale),
or the system fails, which triggers a corrective maintenance action.

@@

At the end of each cycle,
the component information gained during the completed cycle is added to the component knowledge base
by updating the parameters $\nk$ and $\yk$ accordingly,
%using failure and censoring times as of the end of the cycle.
such that $\nkz$ and $\ykz$ for the following cycle account for the (censored) lifetimes observed during the previous cycle.
%We assume that both planned and unplanned maintenance action takes negligible time,
We assume that both a planned and unplanned maintenance action results in an (as good as) new system state by replacing all components,
such that the system begins a new cycle always under the same conditions.
Replacement schemes that do not replace all components would require to account for the different ages of components in the system
at the start of a new cycle.
While this is in principle possible in our approach,
exploring such selective replacement schemes is out of scope for this paper,
since optimizing over replacement schemes is, in our view, a higly interesting topic on its own,
and we will comment on this in the Outlook (Section~\ref{sec:outlook}).

As we use a one-cycle criterion, the time both planned and unplanned maintenance actions require
does not matter directly for the determination of $\tausnow$.
Downtimes are instead accounted for indirectly via the costs parameters in the trade-off leading to $\tausnow$,
as described next.

@@

Let $\Tsysnow$ be the random variable corresponding to $\Rsysnow(t)$,
giving the (random) system failure time for times $t > \tnow$,
conditioned on all information available at $\tnow$,
and $\fsysnow(t)$ be the corresponding density.
Conditional on the realization $\tsysnow$ of $\Tsysnow$, the unit cost rate is 
\begin{align}
g(\tau \mid \Tsysnow = \tsysnow) &=
\begin{cases}
c_p / \tau     & \text{if } \tsysnow \ge \tnow + \tau \\
c_u / \tsysnow & \text{if } \tsysnow  <  \tnow + \tau \,.
\end{cases}
\label{eq:gtau}
\end{align}
Note that here, $\tau$ is a timespan starting from $\tnow$,
and so is a time on a prospective time scale, where $0$ corresponds to $\tnow$.
In contrast, $\tnow$ and $\tsysnow$ are times on an absolute time scale,
where $0$ corresponds to the time of system start-up.
Taking the expectation over $\Tsysnow$ in \eqref{eq:gtau} leads to the expected unit cost rate being
\begin{align}
\gnow(\tau) &= \E[g(\tau \mid \Tsysnow)] = \frac{c_p}{\tau} \Rsysnow(\tau) + c_u \int_0^\tau \frac{1}{t} \fsysnow(\tnow + t) \dd t\,,
\label{eq:gtnowtau}
\end{align}
again incorporating all that is known at time $\tnow$.

Note that for the integral in \eqref{eq:gtnowtau} to exist, $\E[1/\Tsysnow \mid \Tsysnow > \tnow]$ must exist,
which is a condition for $\fsysnow(\tnow + t)$ for values of $t$ close to $0$ \citep{2006:coolen-schrijner-coolen}.
This restriction probably plays a role in the CBM literature's reluctance to adopt the one-cycle criterion.
For our approach, however, this condition is not relevant,
as we use a discrete approximation of $\Rsysnow(t)$ and $\fsysnow(t)$, respectively
(see Section~\ref{sec:optim} below).

Minimizing $\gnow(\tau)$ leads to $\tausnow$,
the optimal moment of maintenance on a prospective time scale.
(Our procedure is illustrated for a number of current times $\tnow$ in Figure~\ref{fig:ghistfig2}.)
The prospective unit cost rate $\cstarnow = \gnow(\tausnow)$ corresponding to $\tausnow$
thus is the lowest unit cost rate attainable for the remaining lifetime of the system,
i.e., for what happens beyond current time $\tnow$.
Also of interest is the total cost rate at $\tnow$, denoted by $\ctotalnow$.
This gives the expected unit cost rate calculated over the full time since system start-up,
under the assumption that maintenance is scheduled for $\tstarnow = \tnow + \tausnow$.
$\ctotalnow$ generally decreases with $\tnow$ since for larger $\tnow$, maintenance costs are spread over a longer time.
However, when many (or few but critical) components fail, $\ctotalnow$ may increase,
since then, system failure becomes much more likely, leading to a higher $\cstarnow$.
For a numerical example, these relations are depicted in Figure~\ref{fig:tauhistfig2}.

We will describe next how we numerically evaluate \eqref{eq:gtnowtau} and find $\tausnow$
for our choice of component model.
%($\beta_k > 1$ $\forall k = 1,\ldots,K$ sufficient **???**)
%***here, $\Rsysnow(\cdot)$ shifted such that $\tnow = 0$.

@@

%*** not possible / *** to minimize $\gnow(\tau)$ analytically.
***we calculate $\Rsysnow(t)$ on discrete grid from $\tnow$ until some horizon time $\tnow + t_h$.
$t_h$ can be determined by practical considerations,
but generally should reach into the tail of $\Rsysnow(t)$
such that one can be sure to find $\tausnow$.
We calculate $\gnow(\tau)$ on the same grid,
and determine $\tausnow$ as the minimum over this grid.

We approximate the integral in \eqref{eq:gtnowtau} numerically by a sum,
where $\fsysnow(t)$ is calculated via differences of $\Rsysnow(t)$ values on a dense grid.
$\gnow(\tau)$ is likewise evaluated on a dense grid,
and $\tausnow = \arg\min \gnow(\tau)$ is determined as the minimum over the grid.
%The lower index $\tnow$ of the optimal moment of maintenance serves to remind that
%$\tau^*$ depends on $\tnow$, and also on the history of the system.

@@

\begin{figure}
\includegraphics[width=\textwidth]{tauhistfig2}
\caption{$\tausnow$, $\tstarnow = \tnow + \tausnow$, $\cstarnow = \gnow(\tausnow)$,
and the total unit cost rate $\ctotalnow$ as functions of $\tnow$
for the system depicted in Figure~\ref{fig:brakesys-layout},
assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$,
and $c_u = 1$, $c_p = 0.2$.
$\tausnow$ (top left panel) first decreases slightly, then remains more or less constant during failure-free periods,
dropping significantly at the failures of components $P_2$, $P_3$ and $H$ only.
If $\tprep = 0.5$, the drop of $\tausnow$ from $0.72$ to $0.38$ at $\tnow = 8$ would trigger a maintenance action
at (absolute) time $8.5$.
Since $\tausnow$ does not change dramatically most of the time, $t^*$,
the cost-optimal moment of maintenance on the absolute timescale (top right panel),
steadily increases, with small drops corresponding to drops in $\tausnow$,
indicating that as time progresses, accumulated information indicates that maintenance can be postponed.
Note that $\gnow(\tausnow)$ is the momentary cost rate relating to the expected residual lifetime (lower left panel),
differing from the overall cost rate $\ctotalnow$ (lower right panel).
%For the maintenance action triggered at $\tnow = 8$,
%the overall cost rate is $c_p / 8.5 = 0.024$ if the system does not fail until time $8.5$,
%and between $c_u / 8 = 0.125$ and $c_u / 8.5 = 0.118$ if the system fails.}
At time $8$, the overall expected cost rate for repair scheduled at time $8.38$ is $0.044$,
up from $0.036$ for repair scheduled at time $8.62$, as cost-optimal at time $7.9$.}
\label{fig:tauhistfig2}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{tauhistfig3}
\caption{Illustration of the gains due to the parameter update
assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$.
$\tausnow$ (top left panel) is consistently lower for the non-adaptive algorithm,
same with $t^*$ (top right panel).
The adaptive algorithm recongnizes the higher reliability of system components,
leading to lower current (lower left panel) and total (lower right panels) unit cost rates.}
\label{fig:tauhistfig3}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{tauhist2fig3}
\caption{***early failures: $C_2 = 1$, $C_2 = 3$, $P_2 = 0.5$, $P_3 = 1.5$}
\label{fig:tauhist2fig3}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{tauhist3fig3}
\caption{***very late failures: $C_2 = 10$, $C_3 = 12$, $H = 14$, $P_2 = 8$, $P_3 = 9$}
\label{fig:tauhist3fig3}
\end{figure}

***use simplified brake system from ASCE-ASME paper,
different example histories (when do components fail?)

***In current graphs,
prior component model parameters are taken as in Table~\ref{tab:priorparams},
and $c_u = 1$, $c_p = 0.2$. *** plot prior predictive distributions?***

***example figures are with very weak prior info
(see Table~\ref{tab:priorparams}: $\nkz = 1$ or $2$),
things could look different for stronger expert information!

@@

\begin{table}
\centering
\begin{tabular}{crrrrrrr}
  \toprule
$k$ & $\beta_k$ & $\E[T_i^k]$ & $\ykz$ & $\nkz$ \\
  \midrule
M & $2.5$ & $5$\rule{1.5ex}{0ex} & $75.4$ & $2$\rule{1ex}{0ex} \\
H & $1.2$ & $2$\rule{1.5ex}{0ex} & $ 2.5$ & $1$\rule{1ex}{0ex} \\
C & $2  $ & $8$\rule{1.5ex}{0ex} & $81.5$ & $1$\rule{1ex}{0ex} \\
P & $1.5$ & $3$\rule{1.5ex}{0ex} & $ 6.1$ & $1$\rule{1ex}{0ex} \\
  \bottomrule
\end{tabular}
\caption{Prior parameters for the four component types as used in the numeric examples.}
\label{tab:priorparams}
\end{table}
